General purpose gene annotation using deep learning

### 2019-12-23 paper/main.tex
paper

\section{Approach}
We seek to show a path for improving on current HMM-based methods both in performance and in the ability to generalize. To accomplish this, we use deep neural networks, which have been shown to have the potential to be superior in flexibility and accuracy to traditional machine learning methods when detecting complex patterns in variety of fields. Our model uses the raw genomic sequence as input and produces base pair wise predictions for the present gene annotation. The genomic data was preprocessed with Geenuff \citealp{Denton19}

Equation~(\ref{eq:01}) Text Text Text Text Text Text  Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
.....

\begin{methods}
\section{Methods}

>>>>

\section{Approach}
Helixer is a set of tested guidelines for training and utilizing a general purpose gene annotation model for eukaryotic genomes. We demonstrate the effectiveness of this approach by training a single model for animals (phylogenetic names?) and plants respectively, which was then evaluated on more than 190 genomes in the animal case and 70 genomes for the plant model. We leverage modelling techniques from the field of deep learning, which has been shown to have the potential to be superior in flexibility and accuracy to traditional machine learning methods in a variety of fields. Our model expects the raw genomic sequence as input and produces base pair wise predictions as output.

\begin{methods}
\section{Methods}
The genomic data was preprocessed with Geenuff \citealp{Denton19}
